---
title: "linear model from Web"
author: "Wilhelmus Elersich"
date: "Fall 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
scatterplot.1 <- ggplot(data,aes(y=SIMS, x=ARM))
scatterplot.1 + geom_point() + geom_lm()

```


Looking at this scatterplot, it is clear that SIMS positively correlates with ARM.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This numerically confirms that SIMS positively correlates with ARM.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The residual standard error is 1.226. The adjusted R-squared value is 0.467. We shall compare these values to those of other models to determine which on is best at predicting the value of SIMS.

#### Predict at target point
```{r}
mydat <- data.frame(GRIP = 94, ARM = 88)
```
```{r}
predict(model.1, mydat, interval = "prediction")
```
Using the model, we predict that at GRIP = 94 and ARM = 88, SIM = 0.0706 ± 2.427.


#### scatterplot with model fit
```{R}
 scatterplot.1 + geom_point() + geom_lm()
```

## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
scatterplot.2 <- ggplot(data,aes(y=SIMS, x=GRIP))
scatterplot.2 + geom_point() + geom_lm()

```


SIMS also appears to positively correlate with GRIP. 
### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
This confirms that SIMS positively correlates with GRIP, although this correlation value is slightly less than SIMS~ARM.


### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
``` 
We have a standard error of 1.295, and an adjusted R-squared value of 0.4053.

#### predict model.2 at target point

```{r}
predict(model.2, mydat, interval = "prediction")
```
At GRIP = 94 and ARM =88, the model predicts that SIM = -0.536 ± 2.572

#### now add the model fit to our plot for model.2
  
```{R}
 scatterplot.2 + geom_point() + geom_lm()
```

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
SIMS positively correlates with ARM and GRIP
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 


For this model, we have a residual standard error of 1.144, and and adjusted R-squared value of 0.5358

#### predict model.3 at target point
  
```{r}
predict(model.3, mydat, interval = "prediction")
```

This model predicts that GRIP = 94 and ARM = 88, SIMS = 0.150 ± 2.282 

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
```
This test confirms that model.3 is better than model.2, based off the p-value.

### Model.2 vs Model.3
```{r}
anova(model.2,model.3)
```
This test confirms that model.3 is better than model.1, based off the p-value.

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```
From this test, we can conclude that model.1 is better than model.2. The p-value does not exist, because neither of the models are nested in each other, while both model.1 and model.2 are nested in model.3.

## Conclusion

Based off the anova tests, we can rank the models in order of accuracy:  
1. model.3  
2. model.1  
3. model.2  

From the values we have collected, we can further prove this ranking:

model.3: residual standard error = 1.144, adjusted R-squared value = 0.5358, correlation = 0.7326545, and a prediction margin of error of ± 2.282.  

model.2: residual standard error = 1.226, adjusted R-squared value of 0.467, correlation = 0.6860073, and prediction  margin of error of ± 2.427.  

model.1: residual standard error =1.295, adjusted R-squared value of 0.4053, correlation = 0.6398458, and a prediction margin of error of ± 2.572.  

model.3 has the highest correlation and adjusted R-sqaured values, and the lowest errors.

