---
title: "linear model from Web"
author: "Wilhelmus Elersich"
date: "Fall 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
scatterplot.1 <- ggplot(data,aes(y=SIMS, x=ARM))
scatterplot.1 + geom_point() + geom_lm()

```
Looking at this scatterplot, it is clear that SIMS positively correlates with ARM.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This numerically confirms that SIMS positively correlates with ARM.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

#### Predict at target point
```{r}
mydat <- data.frame(ARM = 88)
```
```{r}
predict(model.1, mydat, interval = "prediction")
```
Using the model, we predict that at ARM = 88, sim = 0.0706 ± 2.427.


#### scatterplot with model fit
```{R}
 scatterplot.1 + geom_point() + geom_lm()
```

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

